% --- 第一阶段：天堂之战 ---
\part{aaa}
\chapter{Genesis of War}


% 使用命令 chapteroverview：
% 参数1：标题
% 参数2：列表项
% 参数3：箴言内容
% 参数4：箴言出处
\chapteroverview
    {The Chronicle of the First Era} % #1 标题
    {                                % #2 列表内容
        \item[\color{rubric}\textbullet] \textbf{The Old Ones:} First masters, creators of the Webway.
        \item[\color{rubric}\textbullet] \textbf{The Necrontyr:} Short-lived, bitter race striving for eternity.
        \item[\color{rubric}\textbullet] \textbf{The C'tan:} Star Gods who offered a treacherous gift.
        \item[\color{rubric}\textbullet] \textbf{Biotransference:} Flesh to metal; the birth of the Soulless.
        \item[\color{rubric}\textbullet] \textbf{War in Heaven:} The conflict that broke the Warp.
    }
    {They warred among the stars before Man crawled from the mud. They broke the galaxy, and we inherited the shards.} % #3 箴言
    {Transcribed from Aeldari Mythology} % #4 出处

% ========================================================
%  正文 (Body)
% ========================================================
\lettrine{L}{ong} before the Emperor walked among us, long before the first human looked up at the night sky from Terra, the galaxy was already a graveyard.

To understand the darkness of the 41st Millennium, we must cast our minds back sixty million years, to the \textbf{War in Heaven}. It is here that the seeds of our current damnation were sown.

\newpage
\section{The Masters and the Envious}
In the beginning, there were the \textbf{Old Ones}. 
\sidenote{Archive Note: The Old Ones are described as reptilian or amphibian in nature.}
They were a cold-blooded, wise species who had unlocked the secrets of the universe. They built the \textit{Webway}—a labyrinth of tunnels between the stars that allowed instant travel without touching the dangerous Warp.

But they were not alone. Under the radiation-scorched sun of a hostile star, another race was born: the \textbf{Necrontyr}. Unlike the Old Ones, the Necrontyr's lives were short, painful, and ridden with cancer. They looked at the immortal Old Ones with jealousy, and that jealousy turned to spite.

The Necrontyr declared war. But it was a war they could not win. The Old Ones' mastery of the Webway pushed the Necrontyr back to their irradiated homeworlds.

\section{The Star Gods' Bargain}
Defeated and desperate, the Necrontyr found salvation in the hearts of stars. They discovered ancient entities of pure energy feeding on suns. They named them the **C'tan** (The Star Gods).

The C'tan promised the Necrontyr what they always wanted: immortality and the power to defeat the Old Ones. All they asked for in return was a physical shell to inhabit.

\section{The Biotransference}
The Necrontyr agreed. They marched into the great bio-furnaces. 
\sidenote{Warning: The following text describes a ritual of absolute soullessness.}
Their weak flesh was stripped away, and their consciousness was transferred into living metal bodies. 

They became the **Necrons**. They gained immortality, yes, but they lost their souls. The C'tan feasted on the life energy of an entire race. The Silent King realized too late that he had traded mortality for eternal slavery.

\section{The Galaxy Burns}
With their new metal bodies, the Necrons turned the tide. The Old Ones were slaughtered. In desperation, the Old Ones engineered warrior races: the \textbf{Aeldari} (Psychic Masters) and the \textbf{Krork} (Ancestors of Orks).

The war was so intense, the psychic backlash boiled the calm Sea of Souls, turning it into the raging Warp we fear today.